Real World Manuscript Analyses

### 2022-05-13 RWE/RWE Manuscript analyses_.Rmd
Modify plot, add variables

    TRUE                                                               ~ NA_character_
  )) %>% 
  mutate(best_CRorbetter = case_when(
    best_response == "VGPR" |
      best_response == "PR" |
      best_response == "Others"                    ~ "< CR",
    best_response == "CR or sCR, MRD-" |
      best_response == "CR or sCR, MRD+" |
      best_response == "CR or sCR, MRD unknown"  ~    "CR or better", 
    TRUE                                                               ~ NA_character_
  )) %>%  
  mutate(best_ORRcollapsed = case_when(
    best_response == "Others"                    ~ "< PR",
    best_response == "CR or sCR, MRD-" |
      best_response == "CR or sCR, MRD+" |
      best_response == "CR or sCR, MRD unknown" |  
      best_response == "VGPR" |
      best_response == "PR"                      ~    "PR or better", 
    TRUE                                                               ~ NA_character_
  )) %>% 
  mutate(best_MRD_response = case_when(
    str_detect(`Day 30 MRD (positive vs negative)`, "MRD-") |
      str_detect(`3 Month MRD (positive vs negative)`, "MRD-")         ~ "MRD-",
    str_detect(`Day 30 MRD (positive vs negative)`, "MRD+") |
      str_detect(`3 Month MRD (positive vs negative)`, "MRD+")         ~ "MRD+",
    TRUE                                                               ~ NA_character_
  )) %>% 
  mutate(overall_response = case_when(
    !is.na(best_response)                 ~ "Response",
    is.na(best_response)                  ~ "No response"
  )) %>% 
  mutate(months_at_best_response = case_when(
    best_response == day30_response_group     ~ 1,
    best_response == day90_response_group     ~ 3
  )) %>% 
  mutate(months_at_best_CRresponse = case_when(
    str_detect(best_response, "CR") &
      best_response == day30_response_group     ~ 1,
    str_detect(best_response, "CR") &
      best_response == day90_response_group     ~ 3
  )) %>% 
  # mutate(MRDneg_in_best_response = case_when(
  #   str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD-") |
  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
  #   str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD") |
  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
  #   TRUE                             ~ NA_character_
  # )) %>% 
  # Median follow up
  mutate(time_leukapheresis_fup = 
           interval(
             start = date_of_apheresis, 
             end = `Date of Last Contact`)/
           duration(n=1, units = "days")) %>%
  # Median time from leukapheresis to infusion 
  mutate(time_leukapheresis_infusion = 
           interval(
             start = date_of_apheresis, 
             end = `Date of CAR T infusion (# of days from apharesis to infusion)`)/
           duration(n=1, units = "days")) %>%
  # Code survival
  mutate(pfs_event = case_when(
    is.na(`Date of PD`)                                ~ 0,
    !is.na(`Date of PD`)                               ~ 1,
    TRUE                                               ~ NA_real_
  )) %>% 
  mutate(pfs_time = coalesce(`Date of PD`, `Date of Death`, `Date of Last Contact`)) %>% 
  mutate(days_at_pfs_from_infusion = 
           interval(
             start = date_of_apheresis, 
             end = pfs_time)/
           duration(n=1, units = "months")) %>%

  mutate(os_event = case_when(
    is.na(`Date of Death`)                             ~ 0,
    !is.na(`Date of Death`)                            ~ 1,
    TRUE                                               ~ NA_real_
  )) %>% 
  mutate(os_time = coalesce(`Date of Death`, `Date of Last Contact`)) %>% 
  mutate(days_at_os_from_infusion = 
           interval(
             start = date_of_apheresis, 
             end = os_time)/
           duration(n=1, units = "months"))

@@

```{r}
## Labeling
var_label(cart0) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
                        # tumor_burden ="Tumor burden", 
                        proteasome = "Refractory to Proteasome Inhibitors",
                       immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
                       tripleref="Triple refractory", pentaref="Penta refractory",
                       CRS_any = "Any CRS", CRS_gradecat = "CRS Grade",
                       ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", 
                       `Deletion 17p prior to CAR-T infusion (yes, no)` = "Deletion 17p at Infusion",
                       `t(4:14) prior to CAR-T infusion (yes, no)` = "t(4:14) at Infusion",
                       `t(14:16) prior to CAR-T infusion (yes, no)` = "t(4:16) at Infusion",
                       `Prior auto SCT (yes, no)` = "Prior auto SCT",
                       `Extramedullary Disease? (Yes, No)` = "Extramedullary disease",
                       dara="Refractory to Daratumumab", cytogenetics = "High-risk cytogenetics",
                       male_sex = "Male sex", number_prior_lines_therapy = "Number of prior lines of therapy (4 vs. >4)",
                       cart_cell_dose = "Cell dose (<400 vs. ≥400)", exclusion_criteria = "Number of KarMMa1 exclusion criteria",
                       comorbidities = "Any comorbid conditions", time_leukapheresis_infusion = "Time from leukapheresis to infusion, days",
                       time_leukapheresis_fup = "Time from leukapheresis to end of follow-up, days", 
                       best_ORRcollapsed = "Best ORR at ≤ 90 days", best_CRorbetter = "Best CR or better at ≤ 90 days")

@@

         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         time_leukapheresis_infusion, time_leukapheresis_fup) %>% 
  tbl_summary(
    type = list(
      c(
      `Extramedullary Disease? (Yes, No)`, 
      `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`,
      `High Marrow Burden (>= 50%)`,
    cytogenetics,
    `Deletion 17p prior to CAR-T infusion (yes, no)`,
        `t(4:14) prior to CAR-T infusion (yes, no)`,
        `t(14:16) prior to CAR-T infusion (yes, no)`,
    `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         Blenrep,`BCMA CAR-T on trial`, `Other BCMA trial`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
    `ECOG > or = 2? (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
    `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
    comorbidities,
        `Did patient met criteria for KarMMa1 pre-CAR-T?`
    )
      ~"categorical"),

@@

## Figure 1. Response rate bar graph for day 30, day 90, Best ORR
### Panel A
```{r}
cart0 %>% 
  select(day30_response_group, day90_response_group, best_response) %>% 
  pivot_longer(cols = everything()) %>% 
  filter(!is.na(value)) %>% 
  mutate(value = factor(value, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR", "Others"))) %>% 
  group_by(name, value) %>% 
  summarise(count=n()) %>% 
  mutate(percent=(count/sum(count)*100)
  ) %>% 
  group_by(name) %>% 
  mutate(n = sum(count)) %>% 
  ungroup() %>% 
  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
  mutate(name =  paste0(name,'\nN = ',n)) %>% 
  ggplot(aes(x= name, y= percent, fill= value))+
  geom_bar(stat = "identity")+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
  ylim(0,100)+
  labs(x= NULL)+
  theme_classic()

cart0 %>% 
  select(day30_response_group, day90_response_group, best_response) %>% 
  pivot_longer(cols = everything()) %>% 
  filter(!is.na(value)) %>% 
  mutate(value = factor(value, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR", "Others"))) %>% 
  group_by(name, value) %>% 
  summarise(count=n()) %>% 
  mutate(percent=(count/sum(count)*100)
  ) %>% 
  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
  group_by(name) %>% 
  mutate(n = sum(count)) %>% 
  ungroup() %>% 
  mutate(name =  paste0(name,'\nN = ',n)) %>% 
  ggplot(aes(x= name, y= percent, fill= value))+
  geom_bar(stat = "identity")+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  ylim(0,100)+
  labs(x= NULL)+
  theme_classic()
```

@@

### Panel C: OS Kaplan Meier (from CAR-T infusion)
```{r, fig.width= 6, fig.height=6}
myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
                   data = cart0),
           title = "OS from date of infusion", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "OS probability",
           xlab = "Time (in months)", ggtheme = theme_classic(), palette = c("Set1") 
) + guides(colour = guide_legend(ncol = 2))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

@@

### Panel D: Duration of response graph
Limit to the patients who have a response
```{r}
cart1 <- cart0 %>% 
  filter(!is.na(best_CRorbetter)) %>% 
  mutate(added = case_when(
    day30_response_group %in% c("CR or sCR, MRD-",
                                "CR or sCR, MRD+", 
                                "CR or sCR, MRD unknown",
                                "VGPR", "PR")       ~ 30,
    day90_response_group %in% c("CR or sCR, MRD-",
                                "CR or sCR, MRD+", 
                                "CR or sCR, MRD unknown",
                                "VGPR", "PR")      ~ 90
  )) %>% 
  mutate(response_date = case_when(
    day30_response_group %in% c("CR or sCR, MRD-",
                                "CR or sCR, MRD+", 
                                "CR or sCR, MRD unknown",
                                "VGPR", "PR")       ~ `Date of CAR T infusion (# of days from apharesis to infusion)` + days(30),
    day90_response_group %in% c("CR or sCR, MRD-",
                                "CR or sCR, MRD+", 
                                "CR or sCR, MRD unknown",
                                "VGPR", "PR")      ~ `Date of CAR T infusion (# of days from apharesis to infusion)` + days(90)
    )) %>% 
  mutate(months_at_pfs_from_response =
           interval(
             start = response_date,
             end = pfs_time)/
           duration(n=1, units = "months"))

ggsurvplot(survfit(Surv(months_at_pfs_from_response, pfs_event) ~ 1, 
                   data = cart1),
           title = "Duration of response", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 12),
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "Duration of response (probability)",
           xlab = "Time since earliest response (months)", ggtheme = theme_classic(), palette = c("Set1")  
) + guides(colour = guide_legend(ncol = 2))

survfit(Surv(months_at_pfs_from_response, pfs_event) ~ 1, 
                   data = cart1)
```

>>>>

    TRUE                                                               ~ NA_character_
  )) %>% 
  mutate(best_CRorbetter = case_when(
    best_response == "VGPR" |
      best_response == "PR" |
      best_response == "Others"                    ~ "< CR",
    best_response == "CR or sCR, MRD-" |
      best_response == "CR or sCR, MRD+" |
      best_response == "CR or sCR, MRD unknown"  ~    "CR or better", 
    TRUE                                                               ~ NA_character_
  )) %>%  
  mutate(best_ORRcollapsed = case_when(
    best_response == "Others"                    ~ "< PR",
    best_response == "CR or sCR, MRD-" |
      best_response == "CR or sCR, MRD+" |
      best_response == "CR or sCR, MRD unknown" |  
      best_response == "VGPR" |
      best_response == "PR"                      ~    "PR or better", 
    TRUE                                                               ~ NA_character_
  )) %>% 
  mutate(best_MRD_response = case_when(
    str_detect(`Day 30 MRD (positive vs negative)`, "MRD-") |
      str_detect(`3 Month MRD (positive vs negative)`, "MRD-")         ~ "MRD-",
    str_detect(`Day 30 MRD (positive vs negative)`, "MRD+") |
      str_detect(`3 Month MRD (positive vs negative)`, "MRD+")         ~ "MRD+",
    TRUE                                                               ~ NA_character_
  )) %>% 
  mutate(overall_response = case_when(
    !is.na(best_response)                 ~ "Response",
    is.na(best_response)                  ~ "No response"
  )) %>% 
  mutate(months_at_best_response = case_when(
    best_response == day30_response_group     ~ 1,
    best_response == day90_response_group     ~ 3
  )) %>% 
  mutate(months_at_best_CRresponse = case_when(
    str_detect(best_response, "CR") &
      best_response == day30_response_group     ~ 1,
    str_detect(best_response, "CR") &
      best_response == day90_response_group     ~ 3
  )) %>% 
  # mutate(MRDneg_in_best_response = case_when(
  #   str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD-") |
  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
  #   str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD") |
  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
  #   TRUE                             ~ NA_character_
  # )) %>% 
  # Median follow up
  mutate(time_leukapheresis_fup = 
           interval(
             start = date_of_apheresis, 
             end = `Date of Last Contact`)/
           duration(n=1, units = "days")) %>%
  mutate(time_infusion_fup = 
           interval(
             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
             end = `Date of Last Contact`)/
           duration(n=1, units = "days")) %>%
  # Median time from leukapheresis to infusion 
  mutate(time_leukapheresis_infusion = 
           interval(
             start = date_of_apheresis, 
             end = `Date of CAR T infusion (# of days from apharesis to infusion)`)/
           duration(n=1, units = "days")) %>%
  # Code survival
  mutate(pfs_event = case_when(
    is.na(`Date of PD`)                                ~ 0,
    !is.na(`Date of PD`)                               ~ 1,
    TRUE                                               ~ NA_real_
  )) %>% 
  mutate(pfs_time = coalesce(`Date of PD`, `Date of Death`, `Date of Last Contact`)) %>% 
  mutate(days_at_pfs_from_infusion = 
           interval(
             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
             end = pfs_time)/
           duration(n=1, units = "months")) %>%

  mutate(os_event = case_when(
    is.na(`Date of Death`)                             ~ 0,
    !is.na(`Date of Death`)                            ~ 1,
    TRUE                                               ~ NA_real_
  )) %>% 
  mutate(os_time = coalesce(`Date of Death`, `Date of Last Contact`)) %>% 
  mutate(days_at_os_from_infusion = 
           interval(
             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
             end = os_time)/
           duration(n=1, units = "months"))

@@

```{r}
## Labeling
var_label(cart0) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
                        # tumor_burden ="Tumor burden", 
                        proteasome = "Refractory to Proteasome Inhibitors",
                       immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
                       tripleref="Triple refractory", pentaref="Penta refractory",
                       CRS_any = "Any CRS", CRS_gradecat = "CRS Grade",
                       ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", 
                       `Deletion 17p prior to CAR-T infusion (yes, no)` = "Deletion 17p at Infusion",
                       `t(4:14) prior to CAR-T infusion (yes, no)` = "t(4:14) at Infusion",
                       `t(14:16) prior to CAR-T infusion (yes, no)` = "t(4:16) at Infusion",
                       `Prior auto SCT (yes, no)` = "Prior auto SCT",
                       `Extramedullary Disease? (Yes, No)` = "Extramedullary disease",
                       dara="Refractory to Daratumumab", cytogenetics = "High-risk cytogenetics",
                       male_sex = "Male sex", number_prior_lines_therapy = "Number of prior lines of therapy (4 vs. >4)",
                       cart_cell_dose = "Cell dose (<400 vs. ≥400)", exclusion_criteria = "Number of KarMMa1 exclusion criteria",
                       comorbidities = "Any comorbid conditions", 
                       time_leukapheresis_infusion = "Time from leukapheresis to infusion, days",
                       time_leukapheresis_fup = "Time from leukapheresis to end of follow-up, days", 
                       time_infusion_fup = "Time from infusion to end of follow-up, days", 
                       best_ORRcollapsed = "Best ORR at ≤ 90 days", best_CRorbetter = "Best CR or better at ≤ 90 days")

@@

         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         time_leukapheresis_infusion, time_infusion_fup,
         time_leukapheresis_fup) %>% 
  tbl_summary(
    type = list(
      c(
      `Extramedullary Disease? (Yes, No)`, 
      `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`,
      `High Marrow Burden (>= 50%)`,
    cytogenetics,
    `Deletion 17p prior to CAR-T infusion (yes, no)`,
        `t(4:14) prior to CAR-T infusion (yes, no)`,
        `t(14:16) prior to CAR-T infusion (yes, no)`,
    `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         Blenrep,`BCMA CAR-T on trial`, `Other BCMA trial`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
    `ECOG > or = 2? (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
    `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
    comorbidities,
        `Did patient met criteria for KarMMa1 pre-CAR-T?`
    )
      ~"categorical"),

@@

## Figure 1. Response rate bar graph for day 30, day 90, Best ORR
### Panel A
```{r}
cart0 %>% 
  select(day30_response_group, day90_response_group, best_response) %>% 
  pivot_longer(cols = everything()) %>% 
  filter(!is.na(value)) %>% 
  mutate(value = factor(value, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR", "Others"))) %>% 
  group_by(name, value) %>% 
  summarise(count=n()) %>% 
  mutate(percent=(count/sum(count)*100)
  ) %>% 
  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
  group_by(name) %>% 
  mutate(n = sum(count)) %>% 
  ungroup() %>% 
  mutate(name =  paste0(name,'\nN = ',n)) %>% 
  ggplot(aes(x= name, y= percent, fill= value))+
  geom_bar(stat = "identity")+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
  ylim(0,100)+
  labs(x= NULL)+
  theme_classic()

cart0 %>% 
  select(day30_response_group, day90_response_group, best_response) %>% 
  pivot_longer(cols = everything()) %>% 
  filter(!is.na(value)) %>% 
  mutate(value = factor(value, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR", "Others"))) %>% 
  group_by(name, value) %>% 
  summarise(count=n()) %>% 
  mutate(percent=(count/sum(count)*100)
  ) %>% 
  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
  group_by(name) %>% 
  mutate(n = sum(count)) %>% 
  ungroup() %>% 
  mutate(name =  paste0(name,'\nN = ',n)) %>% 
  ggplot(aes(x= name, y= percent, fill= value))+
  geom_bar(stat = "identity")+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  ylim(0,100)+
  labs(x= NULL)+
  theme_classic()

cart0 %>% 
  select(day30_response_group, day90_response_group, best_response, 
         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
  filter(!is.na(status)) %>% 
  mutate(status = factor(status, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR", "Others"))) %>%
  group_by(any_bcma, response, status) %>% 
  summarise(count=n()) %>% 
  mutate(percent=(count/sum(count)*100)
  ) %>% 
  # Count N 
  group_by(response) %>% 
  mutate(N = sum(count)) %>% 
  ungroup() %>% 
  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
  mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
  mutate(response =  paste0(response,'\nN = ',N)) %>%

  ggplot(aes(x= any_bcma, y= percent, fill= status))+
  geom_bar(stat = "identity")+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
  ylim(0,100)+
  labs(x= NULL)+
  theme_classic()+
  facet_wrap(. ~ response)

cart0 %>% 
  select(day30_response_group, day90_response_group, best_response, 
         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
  filter(!is.na(status)) %>% 
  mutate(status = factor(status, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR", "Others"))) %>%
  group_by(any_bcma, response, status) %>% 
  summarise(count=n()) %>% 
  mutate(percent=(count/sum(count)*100)
  ) %>% 
  # Count N 
  group_by(response) %>% 
  mutate(N = sum(count)) %>% 
  ungroup() %>% 
  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
  mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
  mutate(response =  paste0(response,'\nN = ',N)) %>%

  ggplot(aes(x= any_bcma, y= percent, fill= status))+
  geom_bar(stat = "identity")+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  # geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
  ylim(0,100)+
  theme_classic()+
  facet_wrap(. ~ response)

cart0 %>% 
  select(day30_response_group, day90_response_group, best_response, 
         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
  filter(!is.na(status)) %>% 
  mutate(status = factor(status, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR", "Others"))) %>%
  group_by(any_bcma, response, status) %>% 
  summarise(count=n()) %>% 
  mutate(percent=(count/sum(count)*100)
  ) %>% 
  # Count N 
  group_by(response) %>% 
  mutate(N = sum(count)) %>% 
  ungroup() %>% 
  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
  mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
  mutate(response =  paste0(response,'\nN = ',N)) %>%

  ggplot(aes(x= (interaction(any_bcma, response)), y= percent, fill= status))+
  geom_bar(stat = "identity")+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
  ylim(0,100)+
  labs(x= NULL)+
  theme_classic()

cart0 %>% 
  select(day30_response_group, day90_response_group, best_response, 
         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
  filter(!is.na(status)) %>% 
  mutate(status = factor(status, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR", "Others"))) %>%
  group_by(any_bcma, response, status) %>% 
  summarise(count=n()) %>% 
  mutate(percent=(count/sum(count)*100)
  ) %>% 
  # Count N 
  group_by(response) %>% 
  mutate(N = sum(count)) %>% 
  ungroup() %>% 
  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
  mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
  mutate(response =  paste0(response,'\nN = ',N)) %>%

  ggplot(aes(x= (interaction(any_bcma, response)), y= percent, fill= status))+
  geom_bar(stat = "identity")+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  ylim(0,100)+
  theme_classic()

# a <- cart0 %>% 
#   select(day30_response_group, day90_response_group, best_response, 
#          any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
#   pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
#   filter(!is.na(status)) %>% 
#   mutate(status = factor(status, levels = c("CR or sCR, MRD-",
#                                         "CR or sCR, MRD+",
#                                         "CR or sCR, MRD unknown",
#                                         "VGPR", "PR", "Others"))) %>%
#   group_by(any_bcma, response, status) %>% 
#   summarise(count=n()) %>% 
#   mutate(percent=(count/sum(count)*100)
#   ) %>% 
#   # Count N 
#   group_by(response) %>% 
#   mutate(N = sum(count)) %>% 
#   ungroup() %>% 
#   filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
#   mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
#   mutate(response =  paste0(response,'\nN = ',N))
# 
# b <- a %>% filter(any_bcma == "NO")
# a %>% filter(any_bcma == "YES") %>% 
#   ggplot(aes(x= name, y= percent, fill= value))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9)
#            )+
#   # geom_bar(stat = "identity",
#   #          # position=position_dodge(width=0.9), 
#   #          data= b,
#   #          aes(x= name, y= percent, fill= value), alpha= 0.4)+
#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
#   ylim(0,100)+
#   labs(x= NULL)+
#   theme_classic()
# 
# a %>% filter(any_bcma == "YES") %>% 
#   ggplot(aes(x= name, y= percent, fill= value))+
#   geom_col(stat = "identity",
#            # position=position_dodge(width=0.9)
#            )+
#   geom_col(stat = "identity",
#            # position=position_dodge(width=0.9),
#            data= b,
#            aes(x= name, y= percent, fill= value), alpha= 0.4)+
#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
#   ylim(0,100)+
#   labs(x= NULL)+
#   theme_classic()
```

@@

### Panel C: OS Kaplan Meier (from CAR-T infusion)
```{r, fig.width= 6, fig.height=6}
myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
                   data = cart0),
           title = "OS from date of infusion", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 12),
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "OS probability",
           xlab = "Time (in months)", ggtheme = theme_classic(), palette = c("Set1") 
) + guides(colour = guide_legend(ncol = 2))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

@@

### Panel D: Duration of response graph
Limit to the patients who have a response
```{r}
cart1 <- cart0 %>% 
  filter(!is.na(best_CRorbetter)) %>% 
  mutate(added = case_when(
    day30_response_group %in% c("CR or sCR, MRD-",
                                "CR or sCR, MRD+", 
                                "CR or sCR, MRD unknown",
                                "VGPR", "PR")       ~ 30,
    day90_response_group %in% c("CR or sCR, MRD-",
                                "CR or sCR, MRD+", 
                                "CR or sCR, MRD unknown",
                                "VGPR", "PR")      ~ 90
  )) %>% 
  mutate(response_date = case_when(
    day30_response_group %in% c("CR or sCR, MRD-",
                                "CR or sCR, MRD+", 
                                "CR or sCR, MRD unknown",
                                "VGPR", "PR")       ~ `Date of CAR T infusion (# of days from apharesis to infusion)` + days(30),
    day90_response_group %in% c("CR or sCR, MRD-",
                                "CR or sCR, MRD+", 
                                "CR or sCR, MRD unknown",
                                "VGPR", "PR")      ~ `Date of CAR T infusion (# of days from apharesis to infusion)` + days(90)
    )) %>% 
  mutate(months_at_pfs_from_response =
           interval(
             start = response_date,
             end = pfs_time)/
           duration(n=1, units = "months")) %>% 
  rename(any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`)

ggsurvplot(survfit(Surv(months_at_pfs_from_response, pfs_event) ~ 1, 
                   data = cart1),
           title = "Duration of response", 
           font.main = c(24, "bold", "black"), 
           font.x = c(14, "bold", "black"), font.y = c(14, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 12),
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "Duration of response (probability)",
           xlab = "Time since earliest response (months)", ggtheme = theme_classic(), palette = c("Set1")  
) + guides(colour = guide_legend(ncol = 2))

survfit(Surv(months_at_pfs_from_response, pfs_event) ~ 1, 
                   data = cart1)

# ggsurvplot(survfit(Surv(months_at_pfs_from_response, pfs_event) ~ any_bcma, 
#                    data = cart1),
#            title = "Duration of response", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(14, "bold", "black"), font.y = c(14, "bold", "black"), 
#            legend = "top", legend.title = "Any BCMA therap",
#            legend.labs = c("No", "Yes"),
#            font.legend = c(14, "bold", "black"),
#            font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            xlim = c(0, 12),
#            pval=TRUE,
#            risk.table = TRUE,
#            risk.table.col = "strata",
#            break.time.by = 3,
#            ylab = "Duration of response (probability)",
#            xlab = "Time since earliest response (months)", ggtheme = theme_classic(), palette = c("Set1")  
# ) + guides(colour = guide_legend(ncol = 2))
```
